### 2017-11-22 manuscript.rmd
updated figures. New knit

\* Corresponding author, casey_dunn@brown.edu

@@

>>>>

\* Corresponding author, casey.dunn@yale.edu

@@

![Schematic of the siphonophore *Nanomia bijuga*, oriented with the anterior of the colony at the top, and the ventral side to the left. Adapted from http://commons.wikimedia.org/wiki/File:Nanomia_bijuga_whole_animal_and_growth_zones.svg, drawn by Freya Goetz. (*A*) Overview of the whole mature colony. (*B*) Inset of the nectosomal growth zone with pneumatophore. A series of buds gives rise to nectophores. (*C*) Inset of the siphosomal growth zone. Probuds subdivide to give rise to zooids in repeating-units (cormidia). Cormidial boundaries are marked by a gastrozooid.](figures/Figure2.pdf)
